### 2011-09-16 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \dataset{XMA-p} \\
  Iterations        & 50 \\
  Pool size         & TODO \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

TODO pseudocode

@@

@@

\FOR{$ih \in IHs$}
  \FOR{$file \in $ official test data}
    \FOR{$i = 1 \to 20$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = ih\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

MSH, NTH, XMA-c, XMA-p boring - finds the optimum in the first step

@@

             1       2      3
100-100      20      19     20
100-200      19      18     17
100-1000     4       1      5
OVA1         20      20     20
OVA2         19      13     18
OVA3         17      18     20

@@

TODO remind what Strategy 1 is, list all ratios we will be using, list files we will be using.

@@

TODO summary table

TODO pseudocode

TODO results and interpretation

@@

>>>>

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \dataset{XMA-p} \\
  Iterations        & 50 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

\begin{algorithm}
\caption{Ignoring text data}
\label{listing-experiment-ignore-text-data}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\STATE \textbf{set} ``ignore text data"
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

TODO interpretation - grammar extraction is very similar if not a bit worse, model creation is about 50\% faster.

@@

\FOR{$ih \in IHs$}
  \FOR{$file \in $ official test data}
    \FOR{$i = 1 \to 20$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = ih, limit = 10\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\dataset{MSH}, \dataset{NTH}, \dataset{XMA-c}, \dataset{XMA-p} boring - finds the optimum in the first step

@@

\begin{table}
  \caption{Performance of various IH chains}
  \bigskip
  \label{table-experiments-chained-ihs-tweaking}
  \centering
  \begin{tabular}{l || c | c | c}
    Dataset & Strategy 1 & Strategy 2 & Strategy 3 \\
    \hline
    \dataset{100-100}  & \textbf{20} & 19 & \textbf{20} \\
    \dataset{100-200}  & \textbf{19} & 18 & 17 \\
    \dataset{100-1000} & 4  & 1  & \textbf{5}  \\
    \dataset{OVA1}     & \textbf{20} & \textbf{20} & \textbf{20} \\
    \dataset{OVA2}     & \textbf{19} & 13 & 18 \\
    \dataset{OVA3}     & 17 & 18 & \textbf{20} \\
    \end{tabular}
  \bigskip
  Each cell represents the number of times (out of 20) the strategy found the optimum - more is better.
\end{table}

@@

%         NB class ChainedIHs1Tweak

TODO remind what Strategy 1 is, list all ratios we will be using

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}, \dataset{OVA1}, \dataset{OVA2}, \dataset{OVA3} \\
  Iterations        & 50 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

\begin{algorithm}
\caption{Chained IHs - Tuning}
\label{listing-experiment-chained-ihs-tuning}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$

\STATE $RW \gets \heu{RemoveWorst}$

\FOR{$rrRatio \in \{0, 0.05, 0.1, 0.2, 0.5\}$}
\FOR{$mutRatio \in \{0.05, 0.1, 0.2\}$}
\FOR{$cxRatio \in \{0.05, 0.1, 0.2\}$}
  \STATE $RR \gets \heu{RandomRemoval}(ratio = rrRatio)$
  \STATE $MUT \gets \heu{Mutation}(ratio = mutRatio, limit = 1)$
  \STATE $CX \gets \heu{Crossover}(ratio = cxRatio, limit = 1)$
  \FOR{$file \in \{\dataset{100-100}, \dataset{100-200}, \dataset{100-1000}, \dataset{OVA1}, \dataset{OVA2}, \dataset{OVA3}\}$}
    \FOR{$i = 1 \to 50$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = (\heu{RR}, \heu{MUT}, \heu{RR}, \heu{CX}, \heu{RW})\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

\begin{table}
  \caption{Performance of Strategy 1 depending on parameters - excerpt}
  \bigskip
  \label{table-experiments-chained-ihs-tweaking}
  \centering
  \begin{tabular}{c | c | c || c | c | c | c | c | c}
    \heu{RR} & \heu{MUT} & \heu{CX} & \dataset{100-100} & \dataset{100-1000} & \dataset{100-200} & \dataset{OVA1} & \dataset{OVA2} & \dataset{OVA3} \\
    \hline
    0.2	& 0.2	& 0.2	   & 2749.58	& \textbf{8633.76}	  & 3029.82	& 110.82	& 98.68	& 2413.86 \\
    0.5	& 0.05	& 0.05 & 1031.24	& 10324.46	& 1371.08	& \textbf{71.88}	  & 63.86	& 1282.94 \\
    0.5	& 0.05	& 0.2	 & \textbf{919.74}	  & 10978.58	& 1322.02	& 74.46	  & 62.42	& \textbf{1217.00} \\
    0.5	& 0.1	& 0.2	   & 1002.20	& 11030.64	& \textbf{1288.06}	& 85.22	  & 80.96	& 1480.90 \\
    0.5	& 0.2	& 0.1	   & 1674.78	& 9779.82	  & 2007.42	& 108.14	& \textbf{58.56}	& 1827.46 \\
    \end{tabular}
  \bigskip
  First 3 columns are ratios for specified heuristics. Remaining columns are average run times in ms. Bold are the best times in that column.
\end{table}

TODO interpretation - we calculated average runtimes for each combination of ratios and each file. Then we picked the ratio combination that yielded the lowest average runtimes.

@@

TODO compare this to pure GLPK run - for example for 100-200, we got from TODO seconds to on average 1.3 seconds.
